<small> Supplementary materials for the main submission entitled - <br><br> Clustering time series based on probability distributions across temporal granularities

### 2021-11-09 paper-supplementary.Rmd
tsne with ellipse update

>>>>

```{r prototype-data-pick}
```

```{r assemble}
```

```{r data-pick}
```

```{r all-data}

```{r clustering}
```

```{r groups-24}

```{r tsne-fit}
```

```{r tsne-plot-supplementary, fig.cap="t-SNE summary of selected $24$ prototype customers. Each ellipse corresponds to a group after clustering using our methodology. Few customers are not enclosed inside an ellipse as they are from mixed groups and there are too few points to calculate an ellipse around them. It is important to note that the selection of prototypes is based on only $50$ percentiles, whereas, the clustering is based on all the deciles."}
